### 2017-06-15 manuscript/manuscript.Rmd
Add git-diagram (created with https://www.draw.io)

Version Control Systems (VCS; also known as Source Control Systems) are computer programs designed for tracking changes to computer code, and sharing the code with others. Although initially developed for writing computer code collaboratively[^vcs-collaborate], it is easy to recognize the benefits of VCS for scientific production and collaboration as well. For example, behavioral experiments are often written in a programming language, and can have multiple authors and versions. Keeping track of the versions of the program, and allowing many authors to contribute to it (without breaking the code) are problems that VCSs were specifically designed for. By extension, VCS is easily adopted to other aspects of the research cycle, such as curating data across computers and laboratories, or writing manuscripts with multiple authors, versions, and sources of results.

@@

The core concepts of version control are that contributors to a project create small checkpoints of the changes they make to the source code (or manuscript text, data, etc.), and then submit those changes to the VCS. The VCS maintains a history of all these little checkpoints, and the exact state of the project at each of these checkpoints.

<!-- Insert illustration of VCS about here. -->

@@

>>>>

Version Control Systems (VCS; also known as Source Control Systems) are computer programs designed for tracking changes to computer code, and collaborating on the code with others. Although initially developed for writing code collaboratively[^vcs-collaborate], it is easy to recognize that VCS can also be adopted for scientific production and collaboration. For example, behavioral experiments are often written in a programming language, and can have multiple authors and versions. Keeping track of the versions of the program, and allowing many authors to contribute to it (without breaking the code) are problems that VCSs were specifically designed for. By extension, VCS is easily adopted to other aspects of the research cycle, such as curating data across computers and laboratories, or writing manuscripts with multiple authors, versions, and sources of results.

@@

The core concepts of version control are that contributors to a project create small checkpoints of the changes they make to the source code (or manuscript text, data, etc.), and then submit those changes to the VCS. The VCS maintains a history of all these little checkpoints, and the exact state of the project at each of these checkpoints. See Figure \@ref(fig:git-diagram) for a diagram of the typical VCS workflow.

@@

```{r git-diagram, fig.cap = "A diagram illustrating the typical Git workflow. Verbs indicated in bold text are Git operations and explained in detail in the main text."}
knitr::include_graphics("../data/git-diagram.png")
```
